### 2020-05-05 main.Rmd
method 1

Sequence data were collected from the PHI-Base database version 4.8 [@phibase] by accessing a text dump of the data kindly prepared on request by the team, the file can be accessed at ^[Ruth please provide this file, is there a link in a repo?]. The pipeline in Figure \@ref(fig:effectorcollection) outlines the steps

```{r, effectorcollection, fig.cap="Workflow diagram for collection of effector sequences from the PHI-Base database annotation and cross reference to Uniprot"}
knitr::include_graphics(
  "figures/effectorsequence_collection.png",
                        )
```

@@

The performance of the trained classifiers is dependent on the quality of the input training data, so it was important that as high quality set of annotated effectors as possible was collected. To this end we used PHI-Base [@phibase] as our primary sequence store. Sequences in PHI-Base are human curated from the literature and have therefore been noted in experimental studies. They do not derive from large scale annotations or contain hypothetical or predicted proteins. This attribute makes it ideal for our purposes as the effectors in PHI-Base are those that have been specifially reported as such in the published literature and are not of the class of sequences that are merely suspected of being effectors on the basis of carrying a secretion signal. To collect effector sequences we parsed a whole database text dump of version 4.8 ^[Ruth, who provided the text dump, was it Martin Urban? Where is the file in your repos?], all proteins marked as plant pathogen effectors were filtered with IDs and Uniprot IDs, then the sequence retrieved from UNIPROT. The sequences retrieved can be seen in the data file in this manuscript's repository ('effector_information.txt') ^[Ruth, can you point out where this data file is in your development repository]. Effector sequences were then divided into taxonomic groups as bacterial, fungal or oomycete derived accordingly. The total number of plant effectors per group can be seen in Table \@ref(tab:effsummary). The species and effector count in each group can be seen in Tables \@ref(tab:bacefftable), \@ref(tab:fungiefftable) and \@ref(tab:oomefftable)

>>>>

Sequence data were collected from the PHI-Base database version 4.8 [@phibase] by accessing a text dump of the data kindly prepared on request by the team, the file can be accessed at ^[Ruth please provide this file, is there a link in a repo?]. The pipeline in Figure \@ref(fig:effectorcollection) outlines the steps used. We filtered plant effector proteins and their taxonomic groups and collected sequences from UniProt Release ^[Ruth, can you confirm the UniProt version you accessed and data], using the code in ^[Ruth, can you add the script/workbook URL from your repo here, please]. We created a correspondingly sized data set of non-effectors with secretion signals originating in species matched to those from which the effectors were drawn. We downloaded sequences for randomly selected proteins matching these criteria from  Ensembl databases ^[Ruth, please list the Ensemble data bases you use] using the BioMart tools with the code in ^[Ruth, can you add the script/workbook URL from your repo here, please].

```{r, effectorcollection, fig.cap="Workflow diagram for collection of effector sequences from the PHI-Base database annotation and cross reference to UniProt"}
knitr::include_graphics(
  "figures/effectorsequence_collection.png",
                        )
```

@@

The performance of the trained classifiers is dependent on the quality of the input training data, so it was important that as high quality set of annotated effectors as possible was collected. To this end we used PHI-Base [@phibase] as our primary sequence store. Sequences in PHI-Base are human curated from the literature and have therefore been noted in experimental studies. They do not derive from large scale annotations or contain hypothetical or predicted proteins. This attribute makes it ideal for our purposes as the effectors in PHI-Base are those that have been specifially reported as such in the published literature and are not of the class of sequences that are merely suspected of being effectors on the basis of carrying a secretion signal. To collect effector sequences we parsed a whole database text dump of version 4.8 ^[Ruth, who provided the text dump, was it Martin Urban? Where is the file in your repos?], all proteins marked as plant pathogen effectors were filtered with IDs and UniProt IDs, then the sequence retrieved from UniProt. The sequences retrieved can be seen in the data file in this manuscript's repository ('effector_information.txt') ^[Ruth, can you point out where this data file is in your development repository]. Effector sequences were then divided into taxonomic groups as bacterial, fungal or oomycete derived accordingly. The total number of plant effectors per group can be seen in Table \@ref(tab:effsummary). The species and effector count in each group can be seen in Tables \@ref(tab:bacefftable), \@ref(tab:fungiefftable) and \@ref(tab:oomefftable)
